Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
Remove confusing comments
attempt to use listing package

\startlocaldefs
\setpkgattr{license}{type}{CC@BY} %% CC@BY@NC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% indentation after theorem-like environments - auto
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\newtheorem*{}{} %% unnumbered
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\theoremstyle{plain}
%%\newtheorem{}{}%[]
%%\theoremstyle{definition}
%%\newtheorem{}{}%[]

@@

An RO-Crate for this article\footnote{\url
{https://w3id.org/ro/doi/10.5281/zenodo.5146227}}
is archived at \url{https://doi.org/10.5281/zenodo.5146227}.
\end{abstract}
%
\begin{keyword} %% 1 u.c.
\kwd{Data publishing}
\kwd{data packaging}
\kwd{FAIR}
\kwd{Linked Data}
\kwd{metadata}
\kwd{reproducibility}
\kwd{research object}
\end{keyword}
%
\end{frontmatter}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main text entry area:
% Every *.md file in content/ in order, except 00, 90
\section{Introduction}

@@

\begin{listing}
\includegraphics{210053i02}
\caption{%\qq{}\protect\footnotemark[31]
Simplified\protect\footnote{Recommended properties for types shown in
Listing \ref{lis1} also include
\texttt{affiliation}, \texttt{citation}, \texttt{contactPoint},
\texttt{description},
\texttt{encodingFormat}, \texttt{funder}, \texttt{geo}, \texttt{identifier},
\texttt{keywords},
\texttt{publisher}; these properties and corresponding contextual
entities are
excluded here for brevity. See complete example
\url
{https://www.researchobject.org/2021-packaging-research-artefacts-with-ro-crate/listing1/}.}
RO-Crate metadata file showing the
flattened compacted JSON-LD \texttt{@graph} array containing the data entities
and contextual entities, cross-referenced using \texttt{@id}. The
\texttt{ro-crate-metadata.json} entity self-declares conformance with the
RO-Crate specification using a versioned persistent identifier, further
RO-Crate descriptions are on the root data entity \texttt{./} or any of the
referenced data or contextual entities, as exemplified by the data
entity \texttt{ImageObject} referencing contextual entities for
\texttt{contentLocation} and \texttt{author} that differs from that of the overall
RO-Crate. In this example, \texttt{about} of the CSV data entity reference the
\texttt{ImageObject}, which then take the roles of both a data entity and
contextual entity. While \texttt{Person} entities ideally are identified with
ORCID PIDs as for Josiah, \texttt{\#alice} is here in contrast an RO-Crate
local identifier, highlighting the pragmatic ``just enough'' Linked
Data approach.}\label{lis1}
\end{listing}

@@

% CrEDiT taxonomy:
%
% Conceptualization
% Data curation
% Formal Analysis
% Funding acquisition
% Investigation
% Methodology
% Project administration
% Resources
% Software
% Supervision
% Validation
% Visualization
% Writing - original draft
% Writing - review \& editing

>>>>

\startlocaldefs
\setpkgattr{license}{type}{CC@BY} %% CC@BY@NC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% indentation after theorem-like environments - auto
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\newtheorem*{}{} %% unnumbered
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\theoremstyle{plain}
%%\newtheorem{}{}%[]
%%\theoremstyle{definition}
%%\newtheorem{}{}%[]

% listing style for JSON/JavaScript - adapted from
% https://github.com/ghammock/LaTeX_Listings_JavaScript_ES6
%
% MIT License
% 
% Copyright (c) 2018 Gary Hammock
% 
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
% 
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
% 
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.
% 
\lstdefinelanguage{JSON}{
  morekeywords=[1]{break, continue, delete, else, for, function, if, in,
    new, return, this, typeof, var, void, while, with},
  % Literals, primitive types, and reference types.
  morekeywords=[2]{false, null, true, boolean, number, undefined,
    Array, Boolean, Date, Math, Number, String, Object},
  % Built-ins.
  morekeywords=[3]{eval, parseInt, parseFloat, escape, unescape},
  sensitive,
  morecomment=[s]{/*}{*/},
  morecomment=[l]//,
  morecomment=[s]{/**}{*/}, % JavaDoc style comments
  morestring=[b]',
  morestring=[b]"
}[keywords, comments, strings]
%% end listing style

@@

An RO-Crate for this article\footnote{\url
{https://w3id.org/ro/doi/10.5281/zenodo.5146227}}
is archived at \url{https://doi.org/10.5281/zenodo.5146227}.
\end{abstract}
%
\begin{keyword} %% 1 u.c.
\kwd{Data publishing}
\kwd{data packaging}
\kwd{FAIR}
\kwd{Linked Data}
\kwd{metadata}
\kwd{reproducibility}
\kwd{research object}
\end{keyword}
%
\end{frontmatter}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main text entry area:
\section{Introduction}

@@

\begin{listing}
%\includegraphics{210053i02}
\begin{lstlisting}[style=JSON]
{ "@context": "https://w3id.org/ro/crate/1.1/context",
  "@graph": [
    { "@id": "ro-crate-metadata.json",      
      "@type": "CreativeWork",
      "conformsTo": {"@id": "https://w3id.org/ro/crate/1.1"},
      "about": {"@id": "./"}
    },
    { "@id": "./",
      "@type": "Dataset",
      "name": "A simplified RO-Crate",
      "author": {"@id": "#alice"},
      "license": {"@id": "https://spdx.org/licenses/CC-BY-4.0"},
      "datePublished": "2021-11-02T16:04:43Z",
      "hasPart": [
        {"@id": "survey-responses-2019.csv"},
        {"@id": "https://example.com/pics/5707039334816454031_o.jpg"}
      ]
    },
    { "@id": "survey-responses-2019.csv",
      "@type": "File",
      "about": {"@id": "https://example.com/pics/5707039334816454031_o.jpg"},
      "author": {"@id": "#alice"}
    },
    { "@id": "https://example.com/pics/5707039334816454031_o.jpg",
      "@type": ["File", "ImageObject"],
      "contentLocation": {"@id": "http://sws.geonames.org/8152662/"},
      "author": {"@id": "https://orcid.org/0000-0002-1825-0097"}
    },
    { "@id": "#alice",
      "@type": "Person",
      "name": "Alice"
    },
    { "@id": "https://orcid.org/0000-0002-1825-0097",
      "@type": "Person",
      "name": "Josiah Carberry"
    },
    { "@id": "http://sws.geonames.org/8152662/",
      "@type": "Place",
      "name": "Catalina Park"
    },
    { "@id": "https://spdx.org/licenses/CC-BY-4.0",
      "@type": "CreativeWork",
      "name": "Creative Commons Attribution 4.0"
    }
  ]
}    
\end{lstlisting}    
\caption{%\qq{}\protect\footnotemark[31]
Simplified\protect\footnote{Recommended properties for types shown in
Listing \ref{lis1} also include
\texttt{affiliation}, \texttt{citation}, \texttt{contactPoint},
\texttt{description},
\texttt{encodingFormat}, \texttt{funder}, \texttt{geo}, \texttt{identifier},
\texttt{keywords},
\texttt{publisher}; these properties and corresponding contextual
entities are
excluded here for brevity. See complete example
\url
{https://www.researchobject.org/2021-packaging-research-artefacts-with-ro-crate/listing1/}.}
RO-Crate metadata file showing the
flattened compacted JSON-LD \texttt{@graph} array containing the data entities
and contextual entities, cross-referenced using \texttt{@id}. The
\texttt{ro-crate-metadata.json} entity self-declares conformance with the
RO-Crate specification using a versioned persistent identifier, further
RO-Crate descriptions are on the root data entity \texttt{./} or any of the
referenced data or contextual entities, as exemplified by the data
entity \texttt{ImageObject} referencing contextual entities for
\texttt{contentLocation} and \texttt{author} that differs from that of the overall
RO-Crate. In this crate, \texttt{about} of the CSV data entity reference the
\texttt{ImageObject}, which then take the roles of both a data entity and
contextual entity. While \texttt{Person} entities ideally are identified with
ORCID PIDs as for Josiah, \texttt{\#alice} is here in contrast an RO-Crate
local identifier, highlighting the pragmatic ``just enough'' Linked
Data approach.}\label{lis1}
\end{listing}

@@
